Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages

### 2019-04-19 sattose/paper.tex
Something about the corpus
Added an abstract

\title{Using Refactoring Techniques to Reduce Duplication in Object Oriented Programming Languages}

@@

\begin{abstract}
The Abstract paragraph should be indented $1/4$ inch (2 pica) on both
the left and right-hand margins. Abstract must be centered, bold, and
in point size 12. Two line spaces precede the Abstract. The Abstract
must be limited to one paragraph.
\end{abstract}

>>>>

\title{Using Refactoring Techniques to Reduce Duplication in Object-Oriented Programming Languages}

@@

\begin{abstract}
Duplication in source code can have a major negative impact on the maintainability of source code. There are several techniques that can be used in order to merge clones, reduce duplication and potentially also reduce the total volume of a software system. In this study, we look into the opportunities to aid in the process of refactoring these duplication problems for object-oriented programming languages. Measurements that have been conducted so far have indicated that more than half of the duplication in code is related to each other through inheritance, making it easier to refactor these clones in a clean way. More measurements will be conducted to get a detailed overview of in what contexts clones occur, and what this means for the refactoring processes of these clones. As a desired output, we strive to construct a model that automatically applies refactorings for a large part of the detected duplication problems and implement this model for the Java programming language.
\end{abstract}
